Spin orbit alignment for KELT-7b and HAT-P-56b via Doppler tomography with TRES

### 2016-04-26 paper.tex
V2 Revision post referee comments

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
%\usepackage[T1]{fontenc}
%\usepackage{aecompl}
\usepackage{aas_macros}
%\usepackage{deluxetable}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
%\usepackage{array}
%\usepackage{lineno}
\usepackage{ifthen}
%\usepackage{rotating}
\usepackage{lscape}
\usepackage{placeins}
%\usepackage{subcaption}
%\usepackage{caption}
\usepackage{longtable}

@@

\date{Accepted XXX.  Received XXX; in original form XXX}

@@

\begin{abstract}
We present Doppler tomographic analyses for the spectroscopic transits of KELT-7b and HAT-P-56b, two hot-Jupiters orbiting rapidly rotating F-dwarf host stars. These include analyses of archival TRES observations for KELT-7b, and a new TRES transit observation of HAT-P-56b. We report spin-orbit aligned geometries for KELT-7b ($2.8_{-0.6}^{+0.6}\,^\circ$) and HAT-P-56b ($1_{-2}^{+4}\,^\circ$). The host stars KELT-7 and HAT-P-56 are among some of the most rapidly rotating planet-hosting stars known. We examine the tidal re-alignment model for the evolution of the spin-orbit angle in the context of the spin rates of these stars. We find no evidence that the rotation rates of KELT-7 and HAT-P-56 have been modified by star-planet tidal interactions, suggesting that the spin-orbit angle of systems around these hot stars may represent their primordial configuration. In fact, KELT-7 and HAT-P-56 are two of three systems in super-synchronous, spin-orbit aligned states, where the rotation periods of the host stars are faster than the orbital periods of the planets.
\end{abstract}

@@

The observed population of hot-Jupiters is thought to have migrated inward after their formation. The angle between the spin axis of the star and the orbit normal of the hot-Jupiter is a useful probe for the migration history of the planet. In the most simple interpretation, planets found in well-aligned orbits are thought to have migrated in the protoplanetary disk via planet-gas interactions \citep[e.g.][]{1996Natur.380..606L}, while those found in high obliquity orbits underwent dynamical interactions, such as planet-planet scattering \citep[e.g.][]{1996Sci...274..954R}, Kozai-Lidov induced eccentricity migration \citep[e.g.][]{2003ApJ...589..605W,2007ApJ...669.1298F}, or were born in primordially tilted disks \citep[e.g.][]{2010MNRAS.401.1505B,2012Natur.491..418B}.  Of the 74 planets with  spin-orbit measurements\footnote{From the Rossiter-McLaughlin sample, a technique that does not impose strong selection biases on the spin-orbit orientation of the systems measured}, 23\% are found in misaligned orbits.

@@

In this study, we present Doppler tomographic analyses to measure the spin-orbit angles of three systems, orbiting rapidly rotating F-type stars. We present a new spectroscopic transit observation for the hot-Jupiter HAT-P-56b \citep{2015AJ....150...85H}, and a re-analysis of archival observations for the hot-Jupiter KELT-7b \citep{2015AJ....150...12B}. The key properties of these systems are presented in Table~\ref{tab:literature_properties}. They all orbit rapidly rotating F-dwarfs, with projected rotational velocities of $70$, and $38\,\text{km\,s}^{-1}$, respectively (see Section~\ref{sec:lsd}). Of all transiting hot-Jupiter hosts known, only the A-stars WASP-33 \citep{2010MNRAS.407..507C}, KOI-13 \citep{2014ApJ...790...30J}, and HAT-P-57 \citep{2015AJ....150..197H} have higher rotation rates.

@@

  \caption{\label{tab:literature_properties}Key properties of the KELT-7 and HAT-P-56 systems from the literature}
  \begin{tabular}{lrr}
    \hline\hline
    &  \textbf{KELT-7} & \textbf{HAT-P-56}\\
    Source & \citet{2015AJ....150...12B} & \citet{2015AJ....150...85H}\\
    \hline
    RA &  05:13:11.0 & 06:45:24.0\\
    DEC &  +33:19:05 & +27:15:08\\
    $V_\text{mag}$ &  8.54 & 10.91\\
    $M_\star \, (M_\odot)$ &  $1.535_{-0.054}^{+0.066}$ & $1.296\pm0.036$ \\
    $R_\star \, (R_\odot)$ &  $1.732_{-0.045}^{+0.043}$ & $1.428\pm0.030$\\
    $T_\text{eff}\,(\text{K})$  &$6789_{-49}^{+50}$ & $6566\pm50$\\
    $v\sin i\,(\text{km\,s}^{-1})$  & $65.0_{-5.9}^{+6.0}$ & $40.06\pm0.50$\\
    $M_p\,(M_\text{Jup})$  & $1.28\pm0.18$ & $1.466\pm0.040$\\
    $R_p\,(R_\text{Jup})$  & $1.533_{-0.047}^{+0.046}$ & $2.18\pm0.25$\\
    Period (days)  & $2.7347749\pm0.0000039$ & $2.7908327\pm0.0000047$\\
    $|\lambda|\,(^\circ)$  & $9.7\pm5.2$ & -\\
    \hline
  \end{tabular}
\end{table*}

The vast majority of known spin-orbit angles have been measured via the Rossiter-McLaughlin effect. When the planet transits the host star, it successively blocks out part of the rotating stellar surface, and thereby induces a net shift in the centroid of the stellar spectral lines, measured as an apparent in-transit radial velocity variation that is dependent on the transit geometry. The Rossiter-McLaughlin effect was observed for KELT-7b by \citet{2015AJ....150...12B}. The system was reported to be in prograde, spin-orbit aligned geometries. The spectral lines of rapidly rotating host stars are severely broadened by rotation, often resulting in blending of individual lines. It is often possible to directly measure the deviation in the rotational broadening kernel of the spectral lines induced by the transiting planet -- a technique known as Doppler tomography. The technique has already been employed to measure the spin-orbit angles of a number of planetary systems \citep{2010MNRAS.403..151C,2010MNRAS.407..507C,2010A&amp;A...523A..52M,2012ApJ...760..139B,2012A&amp;A...543L...5G,2013ApJ...771...11A,2014ApJ...790...30J,2015ApJ...810L..23J,2015AJ....150..197H}. This technique allows us to directly detect the Doppler shadow of the planet, providing a more accurate measurement of the spin-orbit angle, as well improved characterisation of other transit parameters. We present spin-orbit angles for KELT-7b and HAT-P-56b measured via the Doppler tomographic technique.

@@

Spectroscopic observations of the transits were obtained with the Tillinghast Reflector Echelle Spectrograph (TRES) on the 1.5\,m telescope at the Fred Lawrence Whipple Observatory, Mount Hopkins, Arizona, USA. The spectrograph has a resolving power of $\lambda / \Delta \lambda \equiv R = 44000$, sampling the spectral range of 3850-9100\,\AA\, over 51 echelle orders. We use the archival spectroscopic transit data of KELT-7b, originally presented by \citet{2015AJ....150...12B}. The observation was performed on 2013-10-19 UT, a total of 29 spectra were observed, each with 900\,s exposure time made up of three exposures in order to optimize the removal of cosmic rays. The set of spectra achieved an average signal-to-noise per resolution element of $\text{S/N} \sim 160$ over the Mg b line region. Wavelength calibration is achieved by bracketing Th-Ar hollow cathode lamp exposures. The transit of HAT-P-56b was observed on 2016-01-03 UT, with a total of 30 spectra obtained. Similar to the KELT-7b observations, each spectrum was combined from an average of three short exposures, with a total exposure time of 540\,s, achieving an average S/N of $\sim35$. Details of the spectral reduction and extraction can be found in \citet{2010ApJ...720.1118B}.

@@

Extracting the line profile from the spectra of rapidly rotating stars is complicated by the lack of unblended lines. We follow the technique set out in \citet{1997MNRAS.291..658D} and \citet{2010MNRAS.403..151C}, and perform a Least-Squares Deconvolution (LSD) to recover the line broadening kernel of each spectrum. This usually involves deconvolving the observed spectrum against a weighted delta-function line list to derive the broadening kernel of the star. Following \citet{2015AJ....150..197H}, we use unbroadened synthetic spectral templates, rather than weighted delta functions, as the template of the deconvolution. Synthetic spectral templates are generated using the spectral synthesis program SPECTRUM\footnote{\texttt{http://www1.appstate.edu/dept/physics/spectrum/spectrum.html}} \citep{1994AJ....107..742G}, with the ATLAS9 model atmospheres \citep{2004astro.ph..5087C}. We assume no rotation, microturbulence, macroturbulence, and instrumental broadening for the spectral template.

@@

\subsection{Measuring $v\sin i$ from broadening profile}

Spin-orbit angles derived from Doppler tomography and Rossiter-McLaughlin analyses are often degenerate with the rotational velocity of the star. However, $v \sin i$ is difficult to measure from the spectrum due to degenerate effects with other broadening parameters, such as macro turbulence, and the assumed limb darkening parameters. \citet{2012ApJ...757..161T} found the $v\sin i$ estimates from the Stellar Parameter Classification (SPC) pipeline \citep[used in the discovery papers, []{2012Natur.486..375B} were systematic offset from those of the Spectroscopy Made Easy \citep[SME][]{1996A&amp;AS..118..595V} analyses.

To check if the $v\sin i$ can be accurately recovered from the combination of broadening factors, we generated a series of spectra with $v\sin i=50\,\text{km\,s}^{-1}$, macroturbulence of 0 to $10\,\text{km\,s}^{-1}$, and instrumental broadening of $6\,\text{km\,s}^{-1}$ (as per TRES resolution). These are deconvolved against an unbroadened template to derive broadening profiles for each test synthetic spectrum (Figure~\ref{fig:vmacro}). We fit the broadening kernel with the convolution of a rotation term \citep[modelled analytically from][]{2005oasp.book.....G} and a Gaussian term to account for macroturbulence \citep[Expected for F-stars at $6500\,\text{K}$ to be $\sim 6\,\text{km\,s}^{-1}$][]{2014MNRAS.444.3592D} and instrumental broadening. This is different to the SPC approach, which cross correlates a series of spectral templates to the observed spectra, and maximises the cross correlation function peak. Figure~\ref{fig:vmacro} shows the $v\sin i$ can be recovered to within $0.2\,\text{km\,s}^{-1}$.

@@

A $v\sin i$ measurement is made for all available TRES out-of-transit spectra of each object. The median and standard deviation of the $v\sin i$ measurements $69.2\pm0.2\,\text{km\,s}^{-1}$, and $35.7\pm0.7\,\text{km\,s}^{-1}$ for KELT-7 and HAT-P-56 respectively  We also derive macroturbulence velocities of $4.3\pm0.3\,\text{km\,s}^{-1}$, and $7.1\pm1.1\,\text{km\,s}^{-1}$ for each star respectively. The $v\sin i$ we derive for KELT-7 is consistent to that from the discovery paper to within errors ($65_{-5.9}^{+6.0}\,\text{km\,s}^{-1}$), while we derive a slower velocity for HAT-P-56 ($40.1\pm0.5\,\text{km\,s}^{-1}$ from discovery page), a difference likely attributed to the incooporation of macroturbulence in our analysis.

@@

The photometric transits were modelled as per \citet{2002ApJ...580L.171M}. Free parameters include the planet-star radius ratio $R_p/R_\star$, normalised orbital distance $a/R_\star$, orbital inclination inc, the transit centre time $T_0$, and period $P$. The quadratic limb darkening parameters for each band are interpolated from \citet{2000A&amp;A...363.1081C} to the atmospheric parameters of each star, and fixed during the global fitting. To account for the long-cadence nature of the HAT-P-56 K2 light curves, we integrated the model over 30-minutes about each time stamp at 10 evenly spaced points. To ensure the per-point photometric uncertainties are accurate, we also inflated the uncertainties such that the reduced $\chi^2$ is at unity when compared against the best fitting model.

To model the Doppler tomographic transit observations, we first created an averaged out-of-transit rotational profile. The `shadow' of the planet is modelled as a Gaussian intrusion to the average rotational profile at each time step. The Gaussian has width of $R_p/R_\star \times v\sin i$, area of $1-f(t)$ (where $f(t)$ is the flux, blocked by the planet, that makes up the transit light curve), centred about $v_p(t)$ (where $v_p(t)$ is the projected rotational velocity for the region of the star occulted by the planet). Given the low S/N of the signal, a Gaussian function is a quick and effective model for the Doppler shadow of the planet \citep[e.g.][]{2016arXiv160200322C}. The parameter $v_p(t)$ is dependent on the spin-orbit angle $|\lambda|$, and the projected rotational velocity of the star $v \sin i$. As instrumental systematics can induce variations to the rotational profile at each time step, at each fitting iteration we also fit for a dilation in the height and width of the rotational profile. An example of the rotational profile fitting, and the Doppler shadow of the planet, are shown in Figure~\ref{fig:vprof_KELT7} (Top). The flux blocked by the planet directly correlates with the area of the Doppler shadow, and we also constructed a transit light curve directly from the Doppler tomographic signal (Figure~\ref{fig:vprof_KELT7} Bottom).

@@

The per point uncertainties in the rotational profile residuals were estimated by taking the standard deviation of the baseline regions of the rotational profile. We accountted for correlated noise in the broadening kernel via a Gaussian Processes approach \citep[e.g.][]{2015AJ....150..197H}. Applications of Gaussian process regression to astronomical signals have been extensively covered in the literature and shown to reliably retrieve model parameters from data-sets influenced by stochastic noise sources \citep[e.g.][]{2012MNRAS.419.2683G,2014MNRAS.445.3401G}. The Gaussian process regression was modelled with the \emph{George} module \citep{2014arXiv1403.6015A}. We employed a radial exponential kernel to model the co-variance $\Sigma_{ij}$ between points $i$, $j$, with velocities $v_{i}$ and $v_{j}$:
\begin{equation}
  \Sigma_{ij} = \sigma_{i}^2 \delta_{ij} + A \exp \left(- \frac{|v_{i}-v_{j}|}{\tau} \right)\,,
\end{equation}
where $\sigma_{i}$ is the per-point uncertainty for point $i$, and $\delta_{ij}$ is the Kronecker delta function.

@@

  \caption{\label{tab:parameters}Derived transit geometry parameters}
  \begin{tabular}{lrr}
    \hline\hline
    & \textbf{KELT-7b} & \textbf{HAT-P-56b}\\
    \hline
    Period (days)  & $2.734780_{-0.000003}^{+0.000003}$ & $2.790833_{-0.000004}^{+0.000004}$ \\
    $T_0$ (BJD)  & $2456355.2293_{-0.0001}^{+0.0001}$ & $2456553.6165_{-0.0004}^{+0.0004}$ \\
    $R_p/R_\star$  & $0.0921_{-0.0004}^{+0.0004}$ & $0.099_{-0.02}^{+0.02}$ \\
    $a/R_\star$  & $5.50_{-0.07}^{+0.06}$ &  $6.7_{-0.4}^{+0.5}$ \\
    $\text{inc}\,(^\circ)$  & $83.8_{-0.2}^{+0.2}$ & $82.6_{-0.6}^{+0.7}$\\
    $|\lambda|\,(^\circ)$  & $2.7_{-0.6}^{+0.6}$ & $8_{-2}^{+2}$\\
    $v\sin i\,(\text{km\,s}^{-1})$  & $69.3_{-0.2}^{+0.2}$ & $36.4_{-0.7}^{+0.7}$\\
    $\ln(A)$  & $-9.17_{-0.04}^{+0.05}$ & $-7.65_{-0.05}^{+0.05}$ \\
    $\ln(\tau)$  & $3.6_{-0.1}^{+0.1}$ & $2.24_{-0.1}^{+0.1}$\\
    $T_\mathrm{eff}$ (K)  & $6510_{-49}^{+51}$& $6568_{-50}^{+53}$\\
    $\log g$  & $4.14_{-0.03}^{+0.03}$& $4.27_{-0.05}^{+0.06}$\\
    \hline
  \end{tabular}
\end{table*}

@@

To test the dependence of our results on choice of Gaussian process co-variance kernel, we also tested an exponential squared kernel:
\begin{equation}
  \Sigma_{ij} = \sigma_{i}^2 \delta_{ij} + A \exp \left(- \frac{(v_{i}-v_{j})^2}{2\tau} \right)\,,
\end{equation}
yielding $|\lambda| = 2.6_{-0.6}^{+0.6}\,^\circ$ for KELT-7b and $|\lambda| = 7_{-2}^{+2}\,^\circ$ for HAT-P-56b.
Using the Matern 3/2 kernel:
\begin{equation}
  \Sigma_{ij} = \sigma_{i}^2 \delta_{ij} + A \left( 1+\sqrt{\frac{3(v_{i}-v_{j})^2}{\tau}} \right) \exp \left(-\sqrt{\frac{3 (v_{i}-v_{j})^2}{\tau}}\right)\,,
\end{equation}
yields $|\lambda| = 2.7_{-0.6}^{+0.6}\,^\circ$ for KELT-7b and $|\lambda| = 8_{-2}^{+2}\,^\circ$ for HAT-P-56b. In each case, the Gaussian process hyper-parameters converged to a solution without the need to apply priors.  To check for the effect of accounting for stochastic noise via Gaussian process, we also modelled the Doppler tomographic observations without allowing for co-variance between points, and derived similar results, but with smaller uncertainties, of $|\lambda|$ of $2.4_{-0.4}^{+0.4}\,^\circ$ for KELT-7b and $6_{1}^{+2}\,^\circ$ for HAT-P-56b.

@@

We find KELT-7b and HAT-P-56b to in spin-orbit aligned geometries, with $|\lambda|$ of $2.8_{-0.6}^{+0.6}\,^\circ$ and $8_{-2}^{+2}\,^\circ$ for the two systems respectively.

>>>>

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
%\usepackage[T1]{fontenc}
%\usepackage{aecompl}
\usepackage{aas_macros}
%\usepackage{deluxetable}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
%\usepackage{array}
%\usepackage{lineno}
\usepackage{ifthen}
%\usepackage{rotating}
\usepackage{lscape}
\usepackage{placeins}
%\usepackage{subcaption}
%\usepackage{caption}
\usepackage{longtable}
\usepackage{hyperref}

@@

\date{Submitted XXX}

@@

\begin{abstract}
We present Doppler tomographic analyses for the spectroscopic transits of KELT-7b and HAT-P-56b, two hot-Jupiters orbiting rapidly rotating F-dwarf host stars. These include analyses of archival TRES observations for KELT-7b, and a new TRES transit observation of HAT-P-56b. We report spin-orbit aligned geometries for KELT-7b ($2.7 \pm 0.6\,^\circ$) and HAT-P-56b ($8 \pm 2\,^\circ$). The host stars KELT-7 and HAT-P-56 are among some of the most rapidly rotating planet-hosting stars known. We examine the tidal re-alignment model for the evolution of the spin-orbit angle in the context of the spin rates of these stars. We find no evidence that the rotation rates of KELT-7 and HAT-P-56 have been modified by star-planet tidal interactions, suggesting that the spin-orbit angle of systems around these hot stars may represent their primordial configuration. In fact, KELT-7 and HAT-P-56 are two of three systems in super-synchronous, spin-orbit aligned states, where the rotation periods of the host stars are faster than the orbital periods of the planets.
\end{abstract}

@@

The observed population of hot-Jupiters is thought to have migrated inward after their formation. The angle between the spin axis of the star and the orbit normal of the hot-Jupiter is a useful probe for the migration history of the planet. In the most simple interpretation, planets found in well-aligned orbits are thought to have migrated in the protoplanetary disk via planet-gas interactions \citep[e.g.][]{1996Natur.380..606L}, while those found in high obliquity orbits underwent dynamical interactions, such as planet-planet scattering \citep[e.g.][]{1996Sci...274..954R}, Kozai-Lidov induced eccentricity migration \citep[e.g.][]{2003ApJ...589..605W,2007ApJ...669.1298F}, or were born in primordially tilted disks \citep[e.g.][]{2010MNRAS.401.1505B,2012Natur.491..418B}.  Of the 74 planets with  spin-orbit measurements\footnote{Measured by the Rossiter-McLaughlin effect, a technique that does not impose strong selection biases on the spin-orbit orientation of the systems measured. Sample selected from R\'{e}ne Heller's Holt-Rossiter-McLaughlin Encyclopedia (\url{http://www2.mps.mpg.de/homes/heller/}). Where multiple spin-orbit angles are quoted, the authors examined the discovery paper and chose the most robust observation. Only hot-Jupiters are included.}, 23\% are found in misaligned orbits.

@@

In this study, we present Doppler tomographic analyses to measure the spin-orbit angles of two systems, orbiting rapidly rotating F-type stars. We present a new spectroscopic transit observation for the hot-Jupiter HAT-P-56b \citep{2015AJ....150...85H}, and a re-analysis of archival observations for the hot-Jupiter KELT-7b \citep{2015AJ....150...12B}. The key properties of these systems are presented in Table~\ref{tab:literature_properties}. They all orbit rapidly rotating F-dwarfs, with projected rotational velocities of $70$, and $38\,\text{km\,s}^{-1}$, respectively (see Section~\ref{sec:lsd}). Of all transiting hot-Jupiter hosts known, only the A-stars WASP-33 \citep{2010MNRAS.407..507C}, KOI-13 \citep{2014ApJ...790...30J}, and HAT-P-57 \citep{2015AJ....150..197H} have higher rotation rates.

@@

  \caption{\label{tab:literature_properties}Key properties of the KELT-7 and HAT-P-56 systems from the literature}
  \begin{tabular}{lrr}
    \hline\hline
    &  \textbf{KELT-7} & \textbf{HAT-P-56}\\
    Source & \citet{2015AJ....150...12B} & \citet{2015AJ....150...85H}\\
    \hline
    RA &  05:13:11.0 & 06:45:24.0\\
    DEC &  +33:19:05 & +27:15:08\\
    $V_\text{mag}$ &  8.54 & 10.91\\
    $M_\star \, (M_\odot)$ &  $1.535_{-0.054}^{+0.066}$ & $1.296\pm0.036$ \\
    $R_\star \, (R_\odot)$ &  $1.732_{-0.045}^{+0.043}$ & $1.428\pm0.030$\\
    $T_\text{eff}\,(\text{K})$  &$6789_{-49}^{+50}$ & $6566\pm50$\\
    $v\sin i\,(\text{km\,s}^{-1})$  & $65.0_{-5.9}^{+6.0}$ & $40.06\pm0.50$\\
    $M_p\,(M_\text{Jup})$  & $1.28\pm0.18$ & $2.18\pm0.25$\\
    $R_p\,(R_\text{Jup})$  & $1.533_{-0.047}^{+0.046}$ & $1.466\pm0.040$\\
    Period (days)  & $2.7347749\pm0.0000039$ & $2.7908327\pm0.0000047$\\
    $|\lambda|\,(^\circ)$  & $9.7\pm5.2$ & -\\
    \hline
  \end{tabular}
\end{table*}

The vast majority of known spin-orbit angles have been measured via the Rossiter-McLaughlin effect. When the planet transits the host star, it successively blocks out part of the rotating stellar surface, and thereby induces a net shift in the centroid of the stellar spectral lines, measured as an apparent in-transit radial velocity variation that is dependent on the transit geometry. The Rossiter-McLaughlin effect was observed for KELT-7b by \citet{2015AJ....150...12B}. The system was reported to be in prograde, spin-orbit aligned geometries. The spectral lines of rapidly rotating host stars are severely broadened by rotation, resulting in blending of individual lines. In such cases it is often possible to directly measure the deviation in the rotational broadening kernel of the spectral lines induced by the transiting planet -- a technique known as Doppler tomography. The technique has already been employed to measure the spin-orbit angles of a number of planetary systems \citep{2010MNRAS.403..151C,2010MNRAS.407..507C,2010A&amp;A...523A..52M,2012ApJ...760..139B,2012A&amp;A...543L...5G,2013ApJ...771...11A,2014ApJ...790...30J,2015ApJ...810L..23J,2015AJ....150..197H}. This technique allows us to directly detect the Doppler shadow of the planet, providing a more accurate measurement of the spin-orbit angle, as well improved characterisation of other transit parameters. We present spin-orbit angles for KELT-7b and HAT-P-56b measured via the Doppler tomographic technique.

@@

Spectroscopic observations of the transits were obtained with the Tillinghast Reflector Echelle Spectrograph (TRES) on the 1.5\,m telescope at the Fred Lawrence Whipple Observatory, Mount Hopkins, Arizona, USA. The spectrograph has a resolving power of $\lambda / \Delta \lambda \equiv R = 44000$, sampling the spectral range of 3850-9100\,\AA\, over 51 echelle orders. We use the archival spectroscopic transit data of KELT-7b, originally presented by \citet{2015AJ....150...12B}. The observation was performed on 2013-10-19 UT, a total of 29 spectra were observed, each with 900\,s exposure time made up of three exposures in order to optimize the removal of cosmic rays. The set of spectra achieved an average signal-to-noise per resolution element of $\text{S/N} \sim 160$ over the Mg b line region. Wavelength calibration is achieved by a sequence of Th-Ar hollow cathode lamp exposures that bracket each 900s exposure. The transit of HAT-P-56b was observed on 2016-01-03 UT, with a total of 30 spectra obtained. Similar to the KELT-7b observations, each spectrum was combined from an average of three short exposures, with a total exposure time of 540\,s, achieving an average S/N of $\sim35$. Details of the spectral reduction and extraction can be found in \citet{2010ApJ...720.1118B}.

@@

Extracting the line profile from the spectra of rapidly rotating stars is complicated by the lack of unblended lines. We follow the technique set out in \citet{1997MNRAS.291..658D} and \citet{2010MNRAS.407..507C}, and perform a Least-Squares Deconvolution (LSD) to recover the line broadening kernel of each spectrum. This usually involves deconvolving the observed spectrum against a weighted delta-function line list to derive the broadening kernel of the star. Following \citet{2015AJ....150..197H}, we use unbroadened synthetic spectral templates, rather than weighted delta functions, as the template of the deconvolution. Synthetic spectral templates are generated using the spectral synthesis program SPECTRUM\footnote{\texttt{http://www1.appstate.edu/dept/physics/spectrum/spectrum.html}} \citep{1994AJ....107..742G}, with the ATLAS9 model atmospheres \citep{2004astro.ph..5087C}. We assume no rotation, microturbulence, macroturbulence, and instrumental broadening for the spectral template.

@@

\subsection{Measuring $v\sin i$ from broadening profile}
\label{sec:vsini}
Spin-orbit angles derived from Doppler tomography and Rossiter-McLaughlin analyses are often degenerate with the rotational velocity of the star. However, $v \sin i$ is difficult to measure from the spectrum due to degenerate effects with other broadening parameters, such as macro turbulence, and the assumed limb darkening parameters. \citet{2012ApJ...757..161T} found the $v\sin i$ estimates from the Stellar Parameter Classification (SPC) pipeline \citep[used in the discovery papers,] []{2012Natur.486..375B} were systematic offset from those of the Spectroscopy Made Easy \citep[SME][]{1996A&amp;AS..118..595V} analyses. Additional systematic offsets in \teff and \logg between the spectral retrieval procedures have been noted \cite[e.g.][]{2012ApJ...757..161T,2013A&A...558A.106M}, but are small enough that the derived line profiles and Doppler tomographic signals are not affected. However, we note that the host star properties, which are part of the global modelling in Section~\ref{sec:modelling}, will affect the final derived stellar properties (e.g. $M_\star$, $R_\star$, and resulting planet properties).

To check if the $v\sin i$ can be accurately recovered from the combination of broadening factors, we generated a series of spectra with $v\sin i=50\,\text{km\,s}^{-1}$, macroturbulence of 0 to $10\,\text{km\,s}^{-1}$, and instrumental broadening of $6\,\text{km\,s}^{-1}$ (as per TRES resolution). These are deconvolved against an unbroadened template to derive broadening profiles for each test synthetic spectrum (Figure~\ref{fig:vmacro}). We fit the broadening kernel with the convolution of a rotation term \citep[modelled analytically from][]{2005oasp.book.....G} and a Gaussian term to account for macroturbulence \citep[expected for F-stars at $6500\,\text{K}$ to be $\sim 6\,\text{km\,s}^{-1}$][]{2014MNRAS.444.3592D} and instrumental broadening. This is different to the SPC approach, which cross correlates a series of spectral templates to the observed spectra, and maximises the cross correlation function peak. Figure~\ref{fig:vmacro} shows the $v\sin i$ can be recovered to within $0.2\,\text{km\,s}^{-1}$.

@@

A $v\sin i$ measurement is made for all available TRES out-of-transit spectra of each object. The median and standard deviation of the $v\sin i$ measurements are $69.2\pm0.2\,\text{km\,s}^{-1}$ and $35.7\pm0.7\,\text{km\,s}^{-1}$ for KELT-7 and HAT-P-56 respectively  We also derive macroturbulence velocities of $4.3\pm0.3\,\text{km\,s}^{-1}$ and $7.1\pm1.1\,\text{km\,s}^{-1}$ for each star respectively. The $v\sin i$ we derive for KELT-7 is consistent to that from the discovery paper to within errors ($65_{-5.9}^{+6.0}\,\text{km\,s}^{-1}$), while we derive a slower velocity for HAT-P-56 ($40.1\pm0.5\,\text{km\,s}^{-1}$ from discovery page), a difference likely attributed to the incorporation of macroturbulence in our analysis.

@@

The photometric transits were modelled as per \citet{2002ApJ...580L.171M}. Free parameters include the planet-star radius ratio $R_p/R_\star$, normalised orbital distance $a/R_\star$, orbital inclination inc, the transit centre time $T_0$, and period $P$. The quadratic limb darkening parameters for each band are taken from \citet{2011A&A...529A..75C}, interpolated using the tools described in \citet{2013PASP..125...83E} to the atmospheric parameters of each star, and fixed during the global fitting. To account for the long-cadence nature of the HAT-P-56 K2 light curves, we integrated the model over 30-minutes about each time stamp at 10 evenly spaced points. To ensure the per-point photometric uncertainties are accurate, we also inflated the uncertainties such that the reduced $\chi^2$ is at unity when compared against the best fitting model.

To model the Doppler tomographic transit observations, we first created an averaged out-of-transit rotational profile. The `shadow' of the planet is modelled as a Gaussian intrusion to the average rotational profile at each time step. The Gaussian has width of $R_p/R_\star \times v\sin i$, area of $1-f(t)$ (where $f(t)$ is the flux, blocked by the planet, that makes up the transit light curve), centred about $v_p(t)$ (where $v_p(t)$ is the projected rotational velocity for the region of the star occulted by the planet). Given the low S/N of the signal, a Gaussian function is a quick and effective model for the Doppler shadow of the planet \citep[e.g.][]{2016arXiv160200322C}. The parameter $v_p(t)$ is dependent on the spin-orbit angle $|\lambda|$, and the projected rotational velocity of the star $v \sin i$. As instrumental systematics can induce variations to the rotational profile at each time step, at each iteration we also fit for a dilation in the height and width of the rotational profile. An example of the rotational profile fitting, and the Doppler shadow of the planet, are shown in Figure~\ref{fig:vprof_KELT7} (Top). The flux blocked by the planet directly correlates with the area of the Doppler shadow, and we also constructed a transit light curve directly from the Doppler tomographic signal (Figure~\ref{fig:vprof_KELT7} Bottom).

@@

The per point uncertainties in the rotational profile residuals were estimated by taking the standard deviation of the baseline regions of the rotational profile. We accounted for correlated noise in the broadening kernel via a Gaussian Processes approach \citep[e.g.][]{2015AJ....150..197H}. Applications of Gaussian process regression to astronomical signals have been extensively covered in the literature and shown to reliably retrieve model parameters from data-sets influenced by stochastic noise sources \citep[e.g.][]{2012MNRAS.419.2683G,2014MNRAS.445.3401G}. The Gaussian process regression was modelled with the \emph{George} module \citep{2014arXiv1403.6015A}. We employed a radial exponential kernel to model the co-variance $\Sigma_{ij}$ between points $i$, $j$, with velocities $v_{i}$ and $v_{j}$:
\begin{equation}
  \Sigma_{ij} = \sigma_{i}^2 \delta_{ij} + A \exp \left(- \frac{|v_{i}-v_{j}|}{\tau} \right)\,,
\end{equation}
where $\sigma_{i}$ is the per-point uncertainty for point $i$, and $\delta_{ij}$ is the Kronecker delta function.

@@

  \caption{\label{tab:parameters}Derived transit geometry parameters}
  \begin{tabular}{lrr}
    \hline\hline
    & \textbf{KELT-7b} & \textbf{HAT-P-56b}\\
    \hline
    Period (days) $^a$ & $2.734780_{-0.000003}^{+0.000003}$& $2.790833_{-0.000004}^{+0.000004}$ \\
    $T_0$ (BJD)  $^a$  & $2456355.2293_{-0.0001}^{+0.0001}$ & $2456553.6164_{-0.0003}^{+0.0003}$ \\
    $R_p/R_\star$  & $0.0922_{-0.0004}^{+0.0004}$ & $0.099_{-0.002}^{+0.002}$ \\
    $a/R_\star$  & $5.50_{-0.06}^{+0.06}$ &  $6.7_{-0.4}^{+0.5}$ \\
    $\text{inc}\,(^\circ)$  & $83.7_{-0.2}^{+0.2}$ & $82.6_{-0.6}^{+0.7}$\\
    $|\lambda|\,(^\circ)$  & $2.7_{-0.6}^{+0.6}$ & $7_{-2}^{+2}$\\
    $v\sin i\,(\text{km\,s}^{-1})$  $^b$  & $69.3_{-0.2}^{+0.2}$ & $36.4_{-0.7}^{+0.7}$\\
    $\ln(A)$  & $-9.17_{-0.04}^{+0.05}$ & $-7.65_{-0.05}^{+0.05}$ \\
    $\ln(\tau)$  & $3.6_{-0.1}^{+0.1}$ & $2.24_{-0.1}^{+0.1}$\\
    $T_\mathrm{eff}$ (K) $^a$  & $6513_{-53}^{+49}$& $6568_{-53}^{+51}$\\
    $\log g$  & $4.14_{-0.03}^{+0.03}$ $^a$ & $4.26_{-0.05}^{+0.06}$\\
    \hline
  \end{tabular}
  \begin{flushleft}
  $^a$ Gaussian priors according to literature values were imposed.\\
  $^b$ Gaussian priors according to $v\sin i$ estimates from Section~\ref{sec:vsini} were imposed.  
  \end{flushleft}
\end{table*}

@@

To test the dependence of our results on choice of Gaussian process co-variance kernel, we also tested an exponential squared kernel:
\begin{equation}
  \Sigma_{ij} = \sigma_{i}^2 \delta_{ij} + A \exp \left(- \frac{(v_{i}-v_{j})^2}{2\tau} \right)\,,
\end{equation}
yielding $|\lambda| = 2.6_{-0.6}^{+0.6}\,^\circ$ for KELT-7b and $|\lambda| = 7_{-2}^{+2}\,^\circ$ for HAT-P-56b.
Using the Matern 3/2 kernel:
\begin{equation}
  \Sigma_{ij} = \sigma_{i}^2 \delta_{ij} + A \left( 1+\sqrt{\frac{3(v_{i}-v_{j})^2}{\tau}} \right) \exp \left(-\sqrt{\frac{3 (v_{i}-v_{j})^2}{\tau}}\right)\,,
\end{equation}
yields $|\lambda| = 2.7_{-0.6}^{+0.6}\,^\circ$ for KELT-7b and $|\lambda| = 8_{-2}^{+2}\,^\circ$ for HAT-P-56b. In each case, the Gaussian process hyper-parameters converged to a solution without the need to apply priors.  To check for the effect of accounting for stochastic noise via Gaussian process, we also modelled the Doppler tomographic observations without allowing for co-variance between points, and derived similar results, but with smaller uncertainties, of $|\lambda|$ of $2.4_{-0.4}^{+0.4}\,^\circ$ for KELT-7b and $6_{+1}^{+2}\,^\circ$ for HAT-P-56b.

@@

We find KELT-7b and HAT-P-56b to in spin-orbit aligned geometries, with $|\lambda|$ of $2.8 \pm 0.6\,^\circ$ and $8 \pm 2\,^\circ$ for the two systems respectively.
